Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-03-19 WSSSPE2_report/WSSSPE2_review.tex
Section 2: line breaks.
Section 3: intro : add a few words.

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research. Our second keynote speaker was Neil Chue Hong
of Software Sustainability Institute. He shined the light on how scientific
software is prevalently driving advances in many science and engineering fields.
Both keynote speeches spawned further discussion among workshop participants on
the crucial notion ``sustainability'' in the theme of our workshop.

>>>>

The workshop featured two keynote addresses. In the opening keynote
presentation, Kaitlin Thaney of the Mozilla Science Lab talked about her
organization's work and policy to enable and support sustainable and
reproducible scientific research through the open web. Our second keynote speaker was Neil Chue Hong
of Software Sustainability Institute. He shined the light on how scientific
software is prevalently driving advances in many science and engineering fields.
Both keynote speeches spawned further discussion among workshop participants on
the crucial notion ``sustainability'' in the theme of our workshop.
